%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{multicol}

\renewcommand{\familydefault}{\sfdefault}

\name{Alexander Lalejini} % Your name
\address{49 Kirk Cauldy Drive \\ Starkville, Mississippi 39759} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(228)~$\cdot$~342~$\cdot$~8299 \\ amlalejini@gmail.com \\ lalejini.com} % Your phone number and email
\begin{document}

%----------------------------------------------------------------------------------------
%	Personal statement SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Awards and Honors}



%\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

	{\bf Mississippi State University} \hfill {\em Present} \\ 
	Degree: Computer Science \\
	Expected Graduation: May 2015 \\
	GPA: 4.0

\end{rSection}

%----------------------------------------------------------------------------------------
%	Publications SECTION
%----------------------------------------------------------------------------------------
%\begin{rSection}{Publications}
%\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Research Experience}

	\begin{rSubsection}{Laboratory for Autonomous Systems Research (LASR)}{May 2014 - Present}{Naval Research Laboratory}{}
	\item Mentor: Dr. Greg Trafton, Dr. Laura Hiatt
	\item I am working on using dynamic context produced by a computational cognitive model to improve a neural network based object recognition system.  
	\end{rSubsection}

	%------------------------------------------------

	\begin{rSubsection}{Center for Advanced Vehicular Systems (CAVS)}{January 2014 - Present}{Mississippi State University}{}
	\item Mentor: Dr. Daniel Carruth, Dr. Cindy Bethel	\item I have worked on the ITAR restricted CRES-GV project, which involved writing software to integrate robotic platforms in a vehicle simulation software package.
	\end{rSubsection}

	%------------------------------------------------

	\begin{rSubsection}{Social, Therapeutic, \& Robotic Systems (STaRS) Laboratory}{August 2013 - Present}{Mississippi State University}{}
	\item Mentor: Dr. Cindy Bethel
	\item I have worked as the project co-lead on the Robot Intent and Control Project.  The project involved developing a system that allows for supervisory command and control of an autonomous robot platform using a variety of interfaces.  This system was used in an experiment that measured the relative success of each interface.
	\end{rSubsection}

	%------------------------------------------------



\end{rSection}


%----------------------------------------------------------------------------------------
%	Employment SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Employment}

	\begin{rSubsection}{Naval Research Laboratory (NRL)}{May 2014 - Present}{NREIP Intern}{Washington, D.C.}
	\item Supervisor: Dr. Greg Trafton, Dr. Laura Hiatt
	\item Summer 2014 undergraduate research position at the Laboratory for Autonomous Systems Research
	\end{rSubsection}

	\begin{rSubsection}{Mississippi State University Computer Science Department}{November 2013 - Present}{Undergraduate Research Assistant}{Mississippi State, MS}
	\item Supervisor: Dr. Cindy Bethel
	\item I work as an undergraduate research assistant in the STaRS lab.
	\end{rSubsection}
	
	\begin{rSubsection}{Jet Propulsion Laboratory (JPL)}{Summer 2012}{USRP Intern}{Pasadena, CA}
	\item Supervisor: William R. Johnson
	\item I provided Earth Science software support; I developed a radiometer calibration application using Enthought Python.  The application coordinated the automation of multiple calibration instruments via serial communication and provided the user with real-time data visualization from the calibration process.
	\end{rSubsection}
	
	\begin{rSubsection}{Mississippi State University Physics Department}{Fall 2011 - Spring 2012}{Undergraduate Research Assistant}{Mississippi State, MS}
	\item Supervisor: Dr. Angelle Tanner
	\item I wrote various data analysis and image processing scripts primarily for data collected at the Palomar Observatory.
	\end{rSubsection}
	
	\begin{rSubsection}{Naval Research Laboratory (NRL)}{Summers of 2011, 2010, 2009}{Computer Clerk (2011), SEAP Intern (2010, 2009)}{John C. Stennis Space Center, Mississippi }
	\item Supervisor: Dr. Bruce Lin 
	\item I worked on a battlespace management interface written using the World Wind Java SDK.  I also implemented a clustering algorithm for use in classifying sparse data points.
	\end{rSubsection}


\end{rSection}

%----------------------------------------------------------------------------------------
%	Skills SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Python, C/C++, Java \\
Software Tools \& Libraries & Robot Operating System (ROS), Enthought Python, Scipy, Numpy \\
Version Control &  GIT\\
Robots & Kobuki TurtleBot 2, Dr. Robot Jaguar\\
Web & PHP, HTML/CSS, SQL\\
Operating Systems & Linux, Windows, Mac OS\\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Awards/Honors SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards and Honors}
	\begin{multicols}{2}
		\begin{itemize}
			\item President's Scholar (Fall 2011 - Present)
			\item Shackouls Honors College
			\item Meritorious Award in Bagley Undergraduate Research Poster Competition (Poster title: Robot Control)

		\end{itemize}
	\end{multicols}
\end{rSection}


%----------------------------------------------------------------------------------------
%	Service SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Service}
	
	\begin{rSubsection}{SWAT Training Participant}{November 2013 - Present}{Mississippi State University}{}
		\item I am a volunteer in monthly training exercises by the Starkville SWAT team in coordination with the STaRS lab.
	\end{rSubsection}
	
	\begin{rSubsection}{National SeaPerch Challenge Volunteer}{May 2014}{Hattiesburg, MS}{}
		\item I was a poolside judge for the Heist Challenge.
	\end{rSubsection}	
	
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
